Regression Cube Analysis of Cohort Study Data

### 2015-06-20 draft.tex
added further feedback from Reviewer 3, fixed cube figure

%% INTERACTION
Rotating with the cube is restricted to the y-axis, preserving the mental map to position individual features.
%%
The cube is always oriented according to the 2D representation, allowing for an easy mental combination of the two representations.
%%
Allowing more degrees of freedom was confusing to our users and also did not add value to the visualization.
%%
Also we provide a zoom functionality using the mouse wheel input.
%%
\paragraph{Cube Slice Selection [3.ZF].}
%%
In order to \emph{Zoom, Filter and Analyze Further}, the user has to navigate to different slices of interest.
%%
We propose two ways to achieve this.
\begin{itemize}
	\item \emph{Applying the slicing metaphor from 3D volume data.}
	%%
	In medical volume data renderings, slicing views are very common to view details on a selected plane in the scene.
	%%
	We employ this technique for selecting cube slices (e.g., by moving a plane via vertical mouse input while pressing the right mouse button).
	%%
	We, however, still display the whole 3D object instead of cutting away information down to the slice position.
	%%
	\design{Early prototypes only provided this method to select a slice of interest, which was inefficient when the user was looking for a specific slice.
	%%
	Hence, an additional method was implemented.
	%%
	}
	%%
	\item \emph{Selecting the slice using a dropdown menu} provides fast access to plane selections when the user already knows the slices of interest.
	%%
\end{itemize}
%%
The currently selected slice is denoted with a semi-transparent gray plane.
%%
The space available from visualizing only the prism generated from the upper half of the cube diagonal is used to display information about the currently selected plane.
%%
The values are projected on this plane to give an overlapping-free view on the data points, which makes it easier to identify the current slice.
%%
\paragraph{2D Mosaic Plot Slice Visualization [4.DD].}
%%
The 2D mosaic visualization (Fig.~\ref{fig:System}c) shows all values below the matrix diagonal of the current slice.
%%
It creates a optical equivalence with the 3D cube.
%%
To reduce visual clutter, the 2D view only shows dimensions, which are retrieved through the correlation-based feature selection.
%%
The free space above the matrix diagonal is used to display the 3D cube.
%%

>>>>

%% INTERACTION
Rotating with the cube is restricted to the y-axis, preserving the mental map to position individual features.
%%
The cube is always oriented according to the 2D representation, allowing for an easy mental combination of the two representations.
%%
Allowing more degrees of freedom was confusing to our users and also did not add value to the visualization.
%%
Also we provide a zoom functionality using the mouse wheel input.
%%
\paragraph{Cube Slice Selection [3.ZF].}
%%
In order to \emph{Zoom, Filter and Analyze Further}, the user has to navigate to different slices of interest.
%%
We propose two ways to achieve this.
\begin{itemize}
	\item \emph{Applying the slicing metaphor from 3D volume data.}
	%%
	In medical volume data renderings, slicing views are very common to view details on a selected plane in the scene.
	%%
	We employ this technique for selecting cube slices (e.g., by moving a plane via vertical mouse input while pressing the right mouse button).
	%%
	We, however, still display the whole 3D object instead of cutting away information down to the slice position.
	%%
	\design{Early prototypes only provided this method to select a slice of interest, which was inefficient when the user was looking for a specific slice.
	%%
	Hence, an additional method was implemented.
	%%
	}
	%%
	\item \emph{Selecting the slice using a dropdown menu} provides fast access to plane selections when the user already knows the slices of interest.
	%%
\end{itemize}
%%
The currently selected slice is denoted with a semi-transparent gray plane.
%%
\design{
Early designs rendered the whole cube, which made it hard to assess the position of the plane.
%%
%Since the regression metrics are mirrored along the diagonal, we decided to use this space to support better identification of the current slice.
Since the regression metrics are mirrored along the diagonal, the space available from visualizing only the prism generated from the upper half of the cube diagonal is used to display information about the currently selected plane.
}
%%
The space available from visualizing only the prism generated from the upper half of the cube diagonal is used to display information about the currently selected plane.
%%
The \magenta{regression metric values} are projected on this plane to provide an overlapping-free view.
%%
This allows for a easier to identify the current slice.
%%
\paragraph{2D Mosaic Plot Slice Visualization [4.DD].}
%%
The 2D mosaic visualization (Fig.~\ref{fig:System}c) shows all values below the matrix diagonal of the current slice.
%%
It creates a optical equivalence with the 3D cube.
%%
To reduce visual clutter, the 2D view only shows dimensions, which are retrieved through the correlation-based feature selection.
%%
The free space above the matrix diagonal is used to display the 3D cube.
%%
